Boosted

### 2015-10-21 boost_tree.rmd
more boosting

all8a$b.rpdol<- all8a$return.pdol 
all8a$b.rpdol<- ifelse(all8a$return.pdol<=0, 1, 0)

@@

all9a<- all8a
write.csv(all9a, 'C:/Users/n9232371/Documents/Consultbusiness/data/all9a.csv')

@@

```{r, echo=FALSE}
set.seed(300)
sample<- sample(1:nrow(all9a), 2/3*nrow(all9a), replace=F)
train<- all9a[sample,]
test<- all9a[-sample,]

@@

#shrinkage should be 0.001, now find number of trees
errors<- double(5)
ntree.seq<-c(2000,3000,4000,6000,8000)
conf.matrix<- list('1' = data.frame(c(0,0), c(0,0)), '2' = data.frame(c(0,0), c(0,0)),
                   '3' = data.frame(c(0,0), c(0,0)), '4' = data.frame(c(0,0), c(0,0)),
                   '5' = data.frame(c(0,0), c(0,0)))
auc<- double(5)
colours <- c("red", "yellow", "green", "blue", "purple")

@@

#4000 trees seems best?

@@

#shrinkage should be 0.001, 4000 trees, now find interaction.depth
errors<- double(5)
int.seq<-c(1,2,3,4,6)
conf.matrix<- list('1' = data.frame(c(0,0), c(0,0)), '2' = data.frame(c(0,0), c(0,0)),
                   '3' = data.frame(c(0,0), c(0,0)), '4' = data.frame(c(0,0), c(0,0)),
                   '5' = data.frame(c(0,0), c(0,0)))
auc<- double(5)
colours <- c("red", "yellow", "green", "blue", "purple")

for(i in 1:5){
        fit<-gbm(as.formula(formula), 
                 data=train, distribution="bernoulli", n.trees= 4000,
                 shrinkage=0.001,interaction.depth=int.seq[i])
        pred<- predict(fit, test, n.tree=4000, type="response")
        errors[i]<- sum(temp)/nrow(test)

@@

errors<- double(4)
obs.seq<-c(10,20,40,50)
conf.matrix<- list('1' = data.frame(c(0,0), c(0,0)), '2' = data.frame(c(0,0), c(0,0)),
                   '3' = data.frame(c(0,0), c(0,0)), '4' = data.frame(c(0,0), c(0,0)))
auc<- double(4)
colours <- c("red", "yellow", "green", "blue")

for(i in 1:4){
        fit<-gbm(as.formula(formula), 
                 data=train, distribution="bernoulli", n.trees= 4000,
                 shrinkage=0.001,interaction.depth=3,
                 n.minobsinnode = obs.seq[i])
        pred<- predict(fit, test, n.tree=4000, type="response")

@@

#go with 10

@@

@@

        #redo train and test
        set.seed = 300
        sample<- sample(1:nrow(all9a), 2/3*nrow(all9a), replace=F)
        train<- all9a[sample,]
        test<- all9a[-sample,]

>>>>

all8a$b.rpdol<- all8a$return.pdol 
all8a$b.rpdol<- ifelse(all8a$return.pdol<=0, 1, 0)
all8a$timespan.cbrt <- ifelse(all8a$timespan.cbrt ==0, 1, all8a$timespan.cbrt)

@@

all9a<- all8a
write.csv(all9a, 'C:/Users/n9232371/Documents/Consultbusiness/data/all9a.csv')
all9a<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all9a.csv')[,-1]

@@

```{r, echo=FALSE}
set.seed(200)
sample<- sample(1:nrow(all9a), 2/3*nrow(all9a), replace=F)
train<- all9a[sample,]
test<- all9a[-sample,]

@@

#shrinkage should be 0.001, now find number of trees

ntree.seq<-c(2000,3000,4000,6000,8000)
conf.matrix<- list('1' = data.frame(c(0,0), c(0,0)), '2' = data.frame(c(0,0), c(0,0)),
                   '3' = data.frame(c(0,0), c(0,0)), '4' = data.frame(c(0,0), c(0,0)),
                   '5' = data.frame(c(0,0), c(0,0)))
auc<- double(5)
colours <- c("red", "yellow", "green", "blue", "purple")

@@

#6000 trees seems best?

@@

#shrinkage should be 0.001, 4000 trees, now find interaction.depth

int.seq<-c(1,2,3,4,6)
conf.matrix<- list('1' = data.frame(c(0,0), c(0,0)), '2' = data.frame(c(0,0), c(0,0)),
                   '3' = data.frame(c(0,0), c(0,0)), '4' = data.frame(c(0,0), c(0,0)),
                   '5' = data.frame(c(0,0), c(0,0)))
auc<- double(5)
colours <- c("red", "yellow", "green", "blue", "purple")

for(i in 1:5){
        fit<-gbm(as.formula(formula), 
                 data=train, distribution="bernoulli", n.trees= 6000,
                 shrinkage=0.001,interaction.depth=int.seq[i])
        pred<- predict(fit, test, n.tree=6000, type="response")

@@

obs.seq<-c(10,20,40,50)
conf.matrix<- list('1' = data.frame(c(0,0), c(0,0)), '2' = data.frame(c(0,0), c(0,0)),
                   '3' = data.frame(c(0,0), c(0,0)), '4' = data.frame(c(0,0), c(0,0)))
auc<- double(4)
colours <- c("red", "yellow", "green", "blue")

for(i in 1:4){
        fit<-gbm(as.formula(formula), 
                 data=train, distribution="bernoulli", n.trees= 6000,
                 shrinkage=0.001,interaction.depth=3,
                 n.minobsinnode = obs.seq[i])
        pred<- predict(fit, test, n.tree=6000, type="response")

@@

#go with 10????!

@@

Can we change timespan to discretised without affecting AUC??

formula<- "b.rpdol~.- mlsto - return.pdol-Year-code.client - code.contact-JD.Second - Business - timespan.cbrt"

conf.matrix<- list('1' = data.frame(c(0,0), c(0,0)), '2' = data.frame(c(0,0), c(0,0)),
                   '3' = data.frame(c(0,0), c(0,0)), '4' = data.frame(c(0,0), c(0,0)))
auc<- double(4)
colours <- c("red", "yellow", "green", "blue")
timeclust.seq<- c(4:7)

x<- dist(all9a$timespan.cbrt, method = 'euclidean')
h.fit<- hclust(x, method = 'ward.D2')

for(i in 1:4){
        #create timespan cluster number column
        all9a$b.timespan.cbrt<- as.factor(cutree(h.fit, k= timeclust.seq[i]))

        set.seed(300)
        sample<- sample(1:nrow(all9a), 2/3*nrow(all9a), replace=F)
        train<- all9a[sample,]
        test<- all9a[-sample,]

        fit<-gbm(as.formula(formula), 
                 data=train, distribution="bernoulli", n.trees= 4000,
                 shrinkage=0.001,interaction.depth=3,
                 n.minobsinnode = 10)
        pred<- predict(fit, test, n.tree=4000, type="response")

#create new data frame 'shrink' to place trees and errors vectors together, then plot:
shrink<- data.frame("shrinkage"= timeclust.seq, "auc" = auc[1:4])
ggplot(shrink, aes(x=shrinkage, y=auc)) + geom_line() + geom_point()+ geom_line()

#takes it down to 0.781 with 5 clusters, not too bad for the ability to use timespan clusters.
#takes it down to 0.783 with 6 clusters

6 timespan clusters seems to give quite good performance :) 0.783. Lets see what those clusters are:

#timespan.cbrt
first.vec<- all9a$timespan.cbrt
x<- dist(first.vec, method = 'euclidean')
fit<- hclust(x, method = 'ward.D2')
plot(fit)
k.choose=6
rect.hclust(fit, k = k.choose)

#assign a cluster number to all rows in data frame
all9a$b.timespan.cbrt<- as.factor(cutree(fit, k= k.choose))

for(i in 1:k.choose){
        print(
        summary(all9a %>% select(b.timespan.cbrt, timespan.cbrt) %>% 
                        filter(b.timespan.cbrt ==i))
        )
}

#clusters roughly break down to 1 day, 3 wks, 2.5m, 9m, 1.5yr, 3 yr, over 3 yr
# in cbrt days this is equivalent to breaks of 0,1,2,7589, 4.2358, 6.5, 8.183, 10.307, 14.1
#make new clusters:
all9a$b.timespan.cbrt<- cut(all9a$timespan.cbrt, 
                            breaks= c(0,2.7589, 4.2358, 6.5, 8.183, 10.307, 14.1), 
                            include.lowest=TRUE, 
                            labels= c("1d-3wk","3wk-2.5m", "2.5m-9m","9m-1.5y","1.5y-3y",">3y"))

set.seed(300)
sample<- sample(1:nrow(all9a), 2/3*nrow(all9a), replace=F)
train<- all9a[sample,]
test<- all9a[-sample,]

fit<-gbm(as.formula(formula), 
        data=train, distribution="bernoulli", n.trees= 4000,
        shrinkage=0.001,interaction.depth=3,
        n.minobsinnode = 10)
pred<- predict(fit, test, n.tree=4000, type="response")

#pROC
pred.p<- roc(test$b.rpdol, pred)
plot.roc(pred.p, col= "pink", print.thres = T)
auc(pred.p)

#reduces AUC to 0.780 :(
#go through tuning process again?

all9a<- all9a %>% select(-timespan.cbrt)
```

@@

        #redo train and test
        set.seed = 200
        sample<- sample(1:nrow(all9a), 2/3*nrow(all9a), replace=F)
        train<- all9a[sample,]
        test<- all9a[-sample,]
